Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-04-23 Manuscript/manuscriptPSsuppl.tex

>>>>

\pagebreak
\section{Calcium density profiles from simulations with \\ POPC:POPS(5:1) mixture}
\todo{This section could benefit from some clarifying text}
\begin{figure}[ht]
  \centering
  \includegraphics[width=10cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixtureALL}
    Number density profiles of Ca$^{2+}$ from POPC:POPS (5:1) mixtures simulated with different force fields. The ion densities are taken along the z-axis that coincides with the bilayer normal. 
  }
  \todo{Should we include also counterions into the plot?} \\
  \todo{It would be helpful to have the panels in the same order as in the main text}
  \todo{Concentration for C36 here is smaller than in main text}

\end{figure}
